Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-07-31 documentation/paper.tex
Use subscripts for position
Defined pressure and acoustic wall cuts

\begin{itemize}
    \item The run was not collected during engineering or testing ($\texttt{run\_type}\neq99$)
    \item Recording was triggered by the camera ($\texttt{trigger\_main}=0$)
    \item Acoustic Parameter is not erroneously large and negative ($log_{10}(\texttt{acoustic\_bubnum})>-100$)
    \item Recorded more than 25 seconds after reaching target pressure ($\texttt{te}>25$)
    \item The bubble position $\chi$ was successfully calculated ($[X, Y, Z]\neq[-100, -100, -100]$)
\end{itemize}

@@

The complete wall cut $WallCut(D)$ is a composition of the fiducial cut $FidWallCut(D)$ (which makes use of the 3D position $\chi$), the pressure cut $PresWallCut(D)$ (which uses data from the pressure transducer), and the acoustic wall cut $AcWallCut(D)$ (which uses the banded Fourier transform $\beta _{8}$).

@@

\begin{itemize}
    \item $Z \leq 523$
    \item Any of the following 4 restrictions are true:
    \begin{itemize}
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 6) \land (0 < Z \leq 400)$
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 6) \land (Z \leq 0) \land (R \leq 100)$
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 13) \land (Z \leq 0) \land (R > 100)$
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 13) \land (Z > 400)$
    \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
    \item The run was not collected during engineering or testing ($\texttt{run\_type}\neq99$)
    \item Recording was triggered by the camera ($\texttt{trigger\_main}=0$)
    \item Acoustic Parameter is not erroneously large and negative ($log_{10}(\texttt{acoustic\_bubnum})>-100$)
    \item Recorded more than 25 seconds after reaching target pressure ($\texttt{te}>25$)
    \item The bubble position $\chi$ was successfully calculated

    ($[\chi_{X}, \chi_{Y}, \chi_{Z}]\neq[-100, -100, -100]$)
\end{itemize}

@@

The complete wall cut $WallCut(D)$ is a composition of the fiducial cut $FidWallCut(D)$ (which makes use of the 3D position $\chi$), the pressure cut $PresWallCut(D)$ (which uses data from the pressure transducer), and the acoustic cut $AcWallCut(D)$ (which uses the banded Fourier transform $\beta _{8}$).

@@

\begin{itemize}
    \item $Z \leq 523$
    \item Any of the following 4 restrictions are true:
    \begin{itemize}
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 6) \land (0 < \chi_{Z} \leq 400)$
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 6) \land (\chi_{Z} \leq 0) \land (R \leq 100)$
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 13) \land (\chi_{Z} \leq 0) \land (R > 100)$
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 13) \land (\chi_{Z} > 400)$
    \end{itemize}
\end{itemize}

\subsubsection{Pressure Cut}

The pressure cut $PresWallCut(D)$ restricts the pressure detected by the pressure transducer, without any position corrections, to be close to 1 ($0.7<\texttt{dytranC}<1.3$). In combination with the acoustic cut $AcWallCut(D)$, this acts as a backup to the fiducial cut.

\subsubsection{Acoustic Cut}

The acoustic cut $AcWallCut(D)$ is defined using the banded Fourier transform $\beta_{8}$ as follows:

$45 < mean(\beta_{8}[(0, 2), (0, 1)]) < 300$

This takes advantage of differences in the frequency distribution (specifically the first and second frequency bands of the first and third piezos) of wall events and non-wall events.
